---
title             : "The title"
shorttitle        : "Title"

author: 
  - name          : "First Author"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Postal address"
    email         : "my@email.com"
  - name          : "Ernst-August Doelle"
    affiliation   : "1,2"

affiliation:
  - id            : "1"
    institution   : "Wilhelm-Wundt-University"
  - id            : "2"
    institution   : "Konstanz Business School"

author_note: |
  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.

  Enter author note here.

abstract: |
  Enter abstract here. Each new line herein must be indented, like this line.
  
keywords          : "keywords"
wordcount         : "X"

bibliography      : ["r-references.bib"]

figsintext        : no
figurelist        : no
tablelist         : no
footnotelist      : no
lineno            : yes
mask              : no
tables            : yes

output            : papaja::apa6_pdf
---

```{r load_packages, include = FALSE}
library("papaja")
library("kableExtra")
```

```{r analysis_preferences}
# Seed for random number generation
set.seed(42)
```

\setlength\extrarowheight{-2pt}

\begin{table}[1]
\caption{My caption}
\label{my-label}
\begin{tabular}{llllll}

Taxonomy     & Domains                & Facets                 & Reliability & Validity & No. of items \\
\midrule
HEXACO       &                        &                        &             &          & 200,100,60   \\
             & Humility               & Sincerity              & 0.66        &          &              \\
             &                        & Fairness               & 0.76        &          &              \\
             &                        & Greed Avoidance        & 0.81        &          &              \\
             &                        & Modesty                & 0.68        &          &              \\
             & Emotionality           & Fearfulness            & 0.7         &          &              \\
             &                        & Anxiety                & 0.64        &          &              \\
             &                        & Dependence             & 0.8         &          &              \\
             &                        & Sentimentality         & 0.7         &          &              \\
             & Extraversion           & Social Self-Esteem     & 0.67        &          &              \\
             &                        & Social Boldness        & 0.76        &          &              \\
             &                        & Sociability            & 0.71        &          &              \\
             &                        & Liveliness             & 0.76        &          &              \\
             & Agreeableness          & Forgivingness          & 0.74        &          &              \\
             &                        & Gentleness             & 0.66        &          &              \\
             &                        & Flexibility            & 0.61        &          &              \\
             &                        & Patience               & 0.79        &          &              \\
             & Conscientiousness      & Organization           & 0.74        &          &              \\
             &                        & Diligence              & 0.7         &          &              \\
             &                        & Perfectionism          & 0.69        &          &              \\
             &                        & Prudence               & 0.69        &          &              \\
             & Openness               & Aesthetic              & 0.66        &          &              \\
             &                        & Inquisitiveness        & 0.66        &          &              \\
             &                        & Creativity             & 0.75        &          &              \\
             &                        & Unconventionality      & 0.52        &          &              \\
\end{tabular}
\end{table}


\begin{table}[1]
\centering
\caption{My caption}
\label{my-label}
\begin{tabular}{llllll}
Taxonomy & Domains           & Facets               & Reliability & Validity & No. of items \\
\midrule
NEO-PI-r &                   &                      &             &          & 240          \\
         & Neuroticism       & Anxiety              & 0.78        &          &              \\
         &                   & Angry Hostility      & 0.75        &          &              \\
         &                   & Depression           & 0.81        &          &              \\
         &                   & Self-Consciousness   & 0.68        &          &              \\
         &                   & Impulsiveness        & 0.7         &          &              \\
         &                   & Vulnerability        & 0.77        &          &              \\
         & Extraversion      & Warmth               & 0.73        &          &              \\
         &                   & Gregariousness       & 0.72        &          &              \\
         &                   & Assertiveness        & 0.77        &          &              \\
         &                   & Activity             & 0.63        &          &              \\
         &                   & Excitement Seeking   & 0.65        &          &              \\
         &                   & Positive Emotions    & 0.73        &          &              \\
         & Openness          & Fantasy              & 0.76        &          &              \\
         &                   & Aesthetics           & 0.76        &          &              \\
         &                   & Feelings             & 0.66        &          &              \\
         &                   & Actions              & 0.58        &          &              \\
         &                   & Ideas                & 0.8         &          &              \\
         &                   & Values               & 0.67        &          &              \\
         & Agreeableness     & Trust                & 0.79        &          &              \\
         &                   & Straightforwardness  & 0.71        &          &              \\
         &                   & Altruism             & 0.75        &          &              \\
         &                   & Compliance           & 0.59        &          &              \\
         &                   & Modesty              & 0.67        &          &              \\
         &                   & Tender-Mindedness    & 0.56        &          &              \\
         & Conscientiousness & Competence           & 0.67        &          &              \\
         &                   & Order                & 0.66        &          &              \\
         &                   & Dutifulness          & 0.62        &          &              \\
         &                   & Achievement Striving & 0.67        &          &              \\
         &                   & Self-Discipline      & 0.75        &          &              \\
         &                   & Deliberation         & 0.71        &          &             
\end{tabular}
\end{table}


\begin{table}[]
\centering
\caption{My caption}
\label{my-label}
\begin{tabular}{llllll}
Taxonomy & Domains               & Facets                 & Reliability & Validity & No. of items \\
BFI-2    &                       &                        & *           &          & 60           \\
         & Extraversion          &                        &             &          &              \\
         &                       & Sociability            & 0.83        &          &              \\
         &                       & Assertiveness          & 0.8         &          &              \\
         &                       & Energy level           & 0.74        &          &              \\
         & Agreeableness         &                        &             &          &              \\
         &                       & Compassion             & 0.68        &          &              \\
         &                       & Respectfulness         & 0.66        &          &              \\
         &                       & Trust                  & 0.75        &          &              \\
         & Conscientiousness     &                        &             &          &              \\
         &                       & Organization           & 0.76        &          &              \\
         &                       & Productiveness         & 0.74        &          &              \\
         &                       & Responsability         & 0.68        &          &              \\
         & Negative Emotionality &                        &             &          &              \\
         &                       & Anxiety                & 0.79        &          &              \\
         &                       & Depression             & 0.74        &          &              \\
         &                       & Emotional Volatility   & 0.7         &          &              \\
         & Open-mindedness       &                        &             &          &              \\
         &                       & Intellectual curiosity & 0.78        &          &              \\
         &                       & Aesthetic Sensitivity  & 0.67        &          &              \\
         &                       & Creative Imagination   & 0.67        &          &             
\end{tabular}
\end{table}




\begin{table}[1]
\begin{tabular}{llllll}
Taxonomy     & Domains                & Facets               & Reliability & Validity & No. of items \\
\midrule
IPIP-NEO-120 &                        &                      &             &          & 120          \\
             & Neuroticism            & Anxiety              & 0.78        &          &              \\
             &                        & Anger                & 0.87        &          &              \\
             &                        & Depression           & 0.85        &          &              \\
             &                        & Self-Consciousness   & 0.74        &          &              \\
             &                        & Inmoderation         & 0.72        &          &              \\
             &                        & Vulnerability        & 0.76        &          &              \\
             & Extraversion           & Friendliness         & 0.81        &          &              \\
             &                        & Gregariousness       & 0.79        &          &              \\
             &                        & Assertiveness        & 0.85        &          &              \\
             &                        & Activity Level       & 0.71        &          &              \\
             &                        & Excitement Seeking   & 0.77        &          &              \\
             &                        & Cheerfulness         & 0.8         &          &              \\
             & Openness to Experience & Imagination          & 0.83        &          &              \\
             &                        & Artistic interests   & 0.76        &          &              \\
             &                        & Emotionality         & 0.69        &          &              \\
             &                        & Adventurousness      & 0.72        &          &              \\
             &                        & Intellect            & 0.75        &          &              \\
             &                        & Liberalism           & 0.64        &          &              \\
             & Agreeableness          & Trust                & 0.86        &          &              \\
             &                        & Morality             & 0.76        &          &              \\
             &                        & Altruism             & 0.76        &          &              \\
             &                        & Cooperation          & 0.73        &          &              \\
             &                        & Modesty              & 0.76        &          &              \\
             &                        & Sympathy             & 0.72        &          &              \\
             & Conscientiousness      & Self-Efficacy        & 0.63        &          &              \\
             &                        & Orderliness          & 0.83        &          &              \\
             &                        & Dutifulness          & 0.69        &          &              \\
             &                        & Achievement-striving & 0.8         &          &              \\
             &                        & Self-Discipline      & 0.73        &          &              \\
             &                        & Cautiousness         & 0.87        &          &             
\end{tabular}
\end{table}



# References
```{r create_r-references}
r_refs(file = "r-references.bib")
```

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id = "refs"></div>
\endgroup
