---
title             : "The Berliner Multi-Facet Personality Inventory: An extensive measure of Big Five personality"
shorttitle        : "BMF-PI"

author: 
  - name          : "Victor Rouco"
    affiliation   : "1,2"
    corresponding : yes    # Define only one corresponding author
    address       : "Postal address"
    email         : "victorrouco@ub.edu"
  - name          : "Anja Cengia"  
    affiliation   : "3"
  - name          : "Matthias Ziegler"
    affiliation   : "3"

affiliation:
  - id            : "1"
    institution   : "Universitat de Barcelona"
  - id            : "2"
    institution   : "Institut de Neurociències de Barcelona"
  - id            : "3"
    institution   : "Humboldt Universität zu Berlin"

author_note: |
  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.

  Enter author note here.

abstract: |
  Enter abstract here. Each new line herein must be indented, like this line.
  
keywords          : "keywords"
wordcount         : "X"

bibliography      : ["IPIP.bib"]

figsintext        : yes
figurelist        : no
tablelist         : yes 
footnotelist      : no
lineno            : yes
mask              : no
floatsintext      : yes
class             : "man"

header-includes:
   - \usepackage{rotating}
   - \usepackage{longtable}
   - \usepackage{changepage}
   
output: 
  papaja::apa6_word
  
  
---
```{r setups, include=FALSE}
knitr::opts_chunk$set(echo = F, message=F, warning=F)
```


```{r load_packages, include = FALSE}
library("papaja")
if(Sys.info()["nodename"]=="imac-de-victor.home"){
  file.copy(from="/Users/victor/Documents/IPIP.bib", to="/Users/victor/Desktop/IPIP_Berliner multi-f/draft/IPIP.bib",
          overwrite=T)
}else{
file.copy(from="/home/victorrouco/Documents/IPIP.bib", to="/home/victorrouco/Desktop/IPIP_git/draft/IPIP.bib",
          overwrite=T)#the mendeley .bib file is in /Documents, this export it automatically to the project file
}

library(here)
library(tidyverse)
library(knitr)
library(xtable)
library(readxl)
library(Hmisc)  #for latexTranslate
library(kableExtra)
library(foreign)
library(MplusAutomation)
library(officer)
library(pander)

options(xtable.floating = T, xtable.comment = FALSE)#figsintext yaml option buggy. change xtable floating instead

setwd(here("tables"))
key <- read_excel("appendix key.xlsx")
cors_req <- read_csv("table5abrev.csv")
setwd(here("data/ETS_IPIP/Datensätze"))

dt<-read_excel("ETS_regression.xlsx")
setwd(here("data/Sample_USA_EFA+CFA/EFA/MAP_PA"))
sub1 <- read_excel("ARI Daten Agreeableness EFA.xls")
setwd(here("data/Sample_USA_EFA+CFA/CFA/Agreeableness"))
sub2 <- read.spss("ARI Data 2009_Agreeableness CFA Sample.sav", to.data.frame=T)
sub2[which(sub2=="-99")] <- NA
sub2 <- sub2[rowSums(is.na(sub2)) != 102, ]


setwd(here("data/Sample_Deutsch_CFA/CFA/Extraversion"))
keyde <- readModels("cfa e1 schüchternheit.out")
de <- read.table("IQIPIP_ohne_Leervaribalen_ohne notes.txt", col.names = unlist(strsplit(keyde$input$variable$names, " ")))

```

```{r analysis_preferences}
# Seed for random number generation
set.seed(42)
#knitr::read_chunk(here::here("table3.R"))
```

# 1. Introduction


Over the last decades, the Five Factor Model as well as the Big Five model have become widely accepted models for describing general attributes of personality. Often the terms are even used synonymously, which is why we will refer to the Big Five from here on. The Big Five is a hierarchical model which describes human individual differences in personality at the dispositional level: one of the most basic, universal, biologically-influenced and stable layers of human inter-individual differences in behavior, cognition and feeling [@McAdams2006a]. Its hierarchical conception is relevant to acknowledge behavior from the most specific (nuances) to the most broad differences in temperament and character (dimensions), through a varying number of mid-level personality characteristics (facets). Most of the research concerning criterion validity of the Big Five inventories has focused on the covariation between the Big Five dimensions and relevant external outcomes. However, specific dispositional characteristics captured on the facet level might be of extreme utility to provide more complex descriptions of individuality and to predict life outcomes to a major extent [@Paunonen2001; @Lounsbury2002; @Ziegler2014]. Unfortunately, the number and nature of the facets below the Big Five is far from being consensual. In fact, different facet level models have been proposed (XXXX). One potential reason for this could be that  many facet level models were developed after a questionnaire version without such a level had been published. Thus, the facets were developed as an elaboration or extension to an existing domain measure. While this has many theoretical advantages it also has the disadvantage of potentially limiting the search space of possible facets. In this work we aim at maximizing this search space and present a personality questionnaire which is broad at the facet level, open-access, and measurement invariant across two different cultures. 

## 1.2. A short history of the Big Five

Francis Galton is credited as being the one who proposed the fundamental lexical hypothesis as a ground from where to describe interpersonal differences in personality. The hypothesis states that every apprehended characteristic in the realm of personality should have its place in the natural language, a corollary derived from this first statement is that the essential features must represent a unique word in the lexical universe of this language. @Galton1884 himself, and later @AllportOdbert1936 and still later @Norman1967, used English dictionaries for a systematic collection of all adjectives which could be related to human personality characteristics. Using exploratory factor analyses on self and other ratings, five broad factors could repeatedly be extracted from the data.

Cattell was one of the first researchers who systematically applied exploratory factor analysis in order to explore personality structure. He inspected the correlation structure of the items in the word lists of his predecessors, finding 16 oblique personality factors, including one factor specifically for intelligence, these factors form the 16-PF. These 16 factors were the primary factors in a hierarchical structure for Cattell (coetany to L.L. Thurstone and undoubtedly influenced by him). Cattell himself viewed personality as a hierarchical structure, containing three layers [@Cattell1956]. The second order factors resemble the Big Five dimensions [@Digman1990].
 
Different researchers followed Cattell in the study of dispositional traits of personality. One of the most influential models was Eysenck‘s Big Three. Grounded on a strong biological basis, Eysenck‘s theory supposed a link between temperament and personality. Its structural proposal concerned at first two big factors, named Neuroticism vs. Emotional stability and Extraversion vs. Introversion. These two dimensions were later  joined by a third factor that Eysenck  called Psychoticism. This label was criticized by others who suggested that a more appropriate term would be psychopathy [@Digman1990]. Eysenck‘s big two are still "alive"" today in the Big Five, and his third factor, psychoticism, can be operationalized as other dimensions within the Big Five: Agreeableness, Conscientiousness and Openness.

A large number of studies have focused on the problem of personality structure resulting in a five factor solution [@Fiske1949; @Norman1967; @TupesChristal1961; @Borgatta1964]. Possibly the two most widely cited works relating to the foundations of the Big Five are those by @Goldberg2006 and @Costa1995. Goldberg can be seen as one of the first who extended research concerning the Big Five, while McRae and Costa‘s importance rests on popularizing the terminology (OCEAN) and the development of one of the most used tools to assess personality based on the Big Five: the NEO-PI. The Big Five dimensions are labeled as follows: I) Extraversion vs. Introversion. II) Agreeableness or Friendliness. III) Conscientiousness or Achievement or Will. IV) Emotional Stability vs. Neuroticism, and V) Openness or Intellect or Culture.

One of the most important features of the Big Five is the fact that it could be replicated in different languages. Research is available in Japanese, Vietnamese, German, Spanish, Greek, and many more [@Schmitt2007]. This finding suggests that the way human beings construe personality is at some point universal and that its basic features are retained within the Big Five. Another essential characteristic relies on its hierarchical nature. The five domains are useful to retain the big picture of personality, maximize the situation consistency and reliably assess difficult subjects such as children. Nonetheless, each dimension is conceptualized as a latent construct formed by more specific narrow factors called facets, which in turn are useful to depict the impact of personality characteristics into specific behaviors and concrete life outcomes. 

The Big Five has proven to be a valid theoretical and empirical model to predict relevant life outcomes. Research such as @OzerBenet2006 or @Roberts2007 has shown that scores for the Big Five dimensions (and their related facets) are able to explain outcomes such as academic and work performance, health, personality disorders, political attitudes and many more. The empirical findings linking Big Five measures to life outcomes have reinforced the concurrent validity of the test scores interpretations. At the same time, the broad nature of the domains has spurned research into the more fine-grained lower order structure of facets.

## 1.3. Facet Structures 

There are a number of models that include a facet structure below the five broad domains. The most widely known model is the one suggested by @Costa1995, the NEO-PI-R model. Other popular models have been suggested for the Big Five Inventory 2 [BFI-2; @SotoJohn2016], the IPIP [@Goldberg2006], and the HEXACO model [@Lee2016], which assumes six broad domains. *Table 1* gives an overview of these different models listing their facets per domain as well as some information regarding their psychometric properties. 

\vspace{5mm}

< Table 1 >

```{r table1, eval=F}
setwd(here("tables"))
table1 <- read_excel("table1.xlsx")
table1 <- table1[,-3]
table1[is.na(table1)]<-" "

 kable(table1, "latex",longtable=T, align="l",linesep="",booktabs=T, caption="Table 1. Influential instruments of the Big Five at the facet level")%>% 
   column_spec(5, width = "12em", bold = F, italic = F) %>% 
   column_spec(1, width = "4em", bold = F, italic = F) %>% 
   column_spec(2, width = "4em", bold = F, italic = F) %>% 
   column_spec(3, width = "8em", bold = F, italic = F) %>% 
   column_spec(4, width = "6em", bold = F, italic = F) %>% 
   kable_styling(latex_options = "repeat_header")  %>% 
   #kable_styling(full_width = T) %>% 
  footnote(c("Reliability: Cronbach's alpha measures, retrieved from references in the reliability column", "Validity: criterion (correlation coefficient) and reference. The most important criterion per reference has been retrieved in the table, one per direct and one per inverse relations. $r$ > .20 to be included in the table"), threeparttable=T, escape=F) 
  
 
pandoc.table(table1, style="grid",split.cells= 5)
  
```


\vspace{5mm}

As shown in *Table 1*, there are different possibilities of facets forming the domains. However, there is still a degree of overlap between the facets covered by the different instruments. @SotoJohn2009  inspected the convergences between the NEO-PI-R and the first version of the BFI, suggesting that two constructs per domain were measured at the facet level by both inventories. The constructs defined by @SotoJohn2009 were: *Altruism* and *Compliance* for Agreeableness;
*Anxiety* and *Depression* for Neuroticism; 
*Order* and *Self-Discipline* for Conscientiousness; 
*Assertiveness* and *Activity* for Extraversion; 
and *Aesthetics* and *Ideas* for Openness. 
The convergence holds for the four instruments listed in *Table 1*, as these ten constructs are covered within the facets for every instrument. Some of the constructs are explicitly covered at the facet level (e.g. Anxiety); meanwhile others are mainly covered by the four instruments, although sometimes implicitly (e.g. Liveliness in HEXACO resembles the “core” construct Activity, present in all other instruments). The reverse is not always true, not every facet within the four instruments is covered by the constructs proposed by @SotoJohn2009. As an example we find Self-Consciousness, a Neuroticism facet defined by the NEO-PI-R and the IPIP-NEO-120, which is not intrinsically tapping at either Anxiety or Depression. The same authors asserted in a later work [@SotoJohn2016] that the Big Five domains *"can be conceptualized and assessed more broadly or more narrowly"*, either focusing in a central facet or in a set of peripheral facets, depending the research interest.

The mid-level layer between domains and facets has also been explored by @DeYoung2007. Their work has focused in the biological consistency of the NEO-PI-R set of facets, thereby proposing a two factor source of variance for each facet of the inventory. In line with their proposal, 
Agreeableness would be composed by *Compassion* and *Politeness*; 
Neuroticism by *Volatility* and *Withdrawal*; 
Conscientiousness by *Industriousness* and *Orderliness*; 
Extraversion by *Enthusiasm* and *Assertiveness*; 
and Openness by *Intellect* and *Openness*. Both @SotoJohn2009 and @DeYoung2007 proposals have many points in common. Maybe the labels *Volatility* and *Withdrawal* for Neuroticism can be suspicious of a different content than *Anxiety* and *Depression*, but when inspected at the item level it is revealed that they are tapping the same components respectively (@DeYoung2007; for item specification).

The nomological network commonly assumed in Big Five questionnaires is drawn from nuances through facets to domains, from more specific to more general. Relying on domains to explain and predict behavior can benefit from ease of interpretability. However, predictions for specific contexts can be enhanced if a more specific set of traits is used. On the other hand, using nuances to predict behavior might yield even stronger predictive ability [@Seeboth2018], but as the number of predictors grows the interpretations become more complex. Facets are on a middle ground between nuances and domains, in a compromise between specificity and sensitivity in the bandwidth-fidelity dilemma. This narrow aggregation both satisfies the specificity of predictions to concrete situations and environments and also enhances the ease of interpretability when summarizing individual personality characteristics. 

Personality measured at the facet level has found to be a strong predictor of a large number of outcomes.
Satisfaction with life (SWL) is one of them. Neuroticism and Extraversion were recognised as the most important personality dimensions in the prediction of subjective satisfaction [@Schimmack2002; @Diener2003]. Lately, @Schimmack2004 observed that the analysis at the facet level outperform the analysis at the domain level. They observed that *Depression* and *Positive Emotions* / *Cheerfulness* explained SWL above and beyond the dimensions they belong to, reaching to a 30% of explained variability of SWL. Correlations in the @Schimmack2004 study ranged in a longitudinal design from *r* = -.57 to *r* = -.49 for the first and from *r* = .51 to *r* = .38 for the second and third. 

Another relevant outcome that has shown to be best predicted with personality at the facet level is academic achievement. The relation of Conscientiousness with academic performance has gained a stable empirical evidence, with correlations ranging from *r* = .20 to *r* = .45 depending in sample specifity [@DeFruyt1996; @Paunonen2001; @Watson2002; @Lievens2002; @Chamorro-Premuzic2003; @Noftle2007; @OConnor2007; @Poropat2009; @Poropat2014]. @DeFruyt1996 hypothesized that volitional facets of Conscientiousness would be more proned to exhibit strong relations with academic achievement. In this line, there is a collection of research which points at relations of GPA scores with facets such as *Achievement-striving* [@Watson2002 *r* = .39; @Chamorro-Premuzic2003; @OConnor2007 *r* ranging from .15 to .39] or *Work drive* [@Lounsbury2002, *r* = .12]. Nonetheless, also other Conscientiousness facets more related to duties or moral driveness have been found to predict significantly GPA scores, like *Self-discipline* [@Watson2002, *r* = .36; @OConnor2007, *r* ranging from  .18 to .25] or *Dutifulness* [@Chamorro-Premuzic2003; @OConnor2007, *r* ranging from .25 to .38]. 
The relation of academic achievement with Openness has been more variant. Following the categories proposed by Costa & McCrae, students which showed both high Conscientiousness and high Openness would be considered "good students". Moreover, those who score high in Openness but not in Conscientiousness were labelled "dreamers" and their performance in academic test is less stable. Some studies found a significant relation between the Openness dimension and academic achievement [@Watson2002, *r* = .18; @Lievens2002, *r* = .09], while some others failed to replicate this findings [@Paunonen2001, *r* = -.04; @Chamorro-Premuzic2003]. Is within this dimension were facet level analysis may be hugely useful. @Paunonen2001 found that the Openness facet of *Understanding* correlates with academic achievement with a *r* = .23. @Noftle2007 identified a set of NEO-PI-R and HEXACO's Openness facets which predicted academic achievement (the HEXACO facets of *Aesthetic*, *Inquisitiveness*, *Creativity* and *Unconventionality*, plus the NEO-PI-R facets of *Fantasy*, *Aesthetics*, *Feelings* and *Ideas*). Oppositely, @Ziegler2014 found that *Openness to ideas* was related positively with work performance, while *Openness to fantasy* was related negatively, potentially masking the overall effect of Opennes over the working performance criterion. In this study we aim to get deep into the research question of which facets are involved in scholastic achievement, using a widely facetted inventory.
Moreover, narrow level analysis seems to improve the predicitive power of personality on academic performance, adding about 10% of explained variance [@Ziegler2010; @OConnor2007; @Lounsbury2004].

Likewise, personality has proven to be a powerful predictor of laboral and educational abseentism [@Chamorro-Premuzic2003; @Judge1997; @Salgado2002]. Research has highlighted the predictive power of personality test over the so-called integrity test when predicting absences [@Ones2003]. Again, most research has focused on the dimensional level, although some researchers suggested that personality assessed at a narrower level would improve the predictive ability of the models [@Salgado2002; @Lounsbury2004]. Nonetheless, few studies have explored this relationship to our knowledge, being @Lounsbury2004 and @Judge1997 the most prominent. @Judge1997 dreported no predictive gain when examining personality at the facet level for the NEO-PI-R composites of Extraversion and Conscientiousness, whereas @Lounsbury2004 found a modest predictive gain of *Work drive* over the Big Five dimensions. Therefore, and despite the conceptual expectation of facets maximizing the predictive ability of personality on abseentism, evidence has manifested in favour of a dimension level analysis. However, it can be arguable that more research needs to be done in this area, preferably using personality inventories which are broad at the facet level.

As described above, facet measures often yield scores that have stronger test-criterion correlations than their respective domain scores. However, facet scores have also been shown to be related to personality disorders. Thus, the combination of a higher fidelity along with the potential clinical relevance of facet scores might open up unique advantages for clinical research. 


## 1.4. The Big Five and Personality Disorders

Personality disorders are steadily shifting from a categorical definition into a continua conceptualization within the clinical realm. This process is not new for personality science history, as the subject itself moved from a qualitatively distinct set of definitions, called types, into a subset of continuous domains in which both normality and extreme tendencies were moving along, named traits. In fact, the new version of the Diagnostic and Statistical Manual of mental disorders, DSM-V, now proposes two different ways of assessing personality disorders: 1) A descriptive model of personality disorders in section II which mimics the former model of assessing personality disorders and; 2) A novel trait model that follows research on the personality scientific domain (In section III), which conceptualizes personality disorders as extreme tendencies located in the continuum of the Big Five domains and facets [@APA2013; @WidigerMullins2009]

This paradigm shift in clinical assessment of personality has led to the construction of the Personality Disorder Inventory [PID-5; @Krueger2012a], a 25-facet and five-dimension self-report inventory, with an informant-report version [@Markon2013]. These five dimensions mirror the Big Five domains, although with a focus on the maladaptative end of the continuum,: I) Detachment (Big Five’s Introversion), II) Antagonism (absence of Big Five’s Agreeableness), III) Disinhibition (absence of Big Five’s Conscientiousness), IV) Negative affect (Big Five’s Neuroticism) and  V) Psychoticism (Absence of Big Five’s Openness). The PID-5 has shown satisfying evidences of criterion validity (...summary). However, the number of facets per domain on the PID-5 is limited.

In line with what has been stated previously for academic achievement, the examination of facets may result in an enhancement of the specificity of assessment when looking at the nature of PDs [@Clark2005; @SamuelWidiger2008]. This improvement of specificity resulted in a predictive gain ranging from 3% to 16% when comparing facets to domains predicting PD in a study by @ClarkReynolds2001. Furthermore, the use of facets may be of extreme utility for those PD whose personality profile is less clear at the domain level. As @SaulsmanPage2004 pointed out, Schizotypal and Obsessive-Compulsive disorders are examples of PD which are not well covered by Big Five domains. A reason for it may be found in a pattern inconsistency of facets within the same dimension or in a lack of coverage for essential characteristics of the PD. For example, aberrant cognitions are essential characteristics of schizotypal disorder and are not covered by some instrument’s facets like the NEO-PI-R [@SaulsmanPage2004; @SamuelWidiger2008]. Likewise, the expected high scores on warmth and low scores on assertiveness could mask the effects of extraversion when predicting Dependent Personality Disorder, following the theoretical correspondence between PD and Big Five facets proposed by @Widiger1994. Moreover, the PID-5 has prompted the elaboration of a number of Five Factor Model Personality Disorders (FFMPD) scales to maximize the facet coverage in relation to specific PDs [@Bagby2018].

Facet analysis and dedicated Big Five questionnaires have been used to solve issues like those mentioned in the last paragraph. We propose to base such research on a broader facet basis. To this end we suggest a general instrument to cover a broad number of facets which could aim for fine grained assessments. 

## This study

We present in this paper an instrument for personality assessment which aims to cover the need for an internationally usable, open source, and differentiated measure at the facet level. Two studies are presented, for each one inspects the factor structure of the instrument in a different sample drawn from a different culture (American vs. German). In the first study we develop the instrument by confirming a factorial structure found after fitting an exploratory factor analysis. Reliability indices are provided for the facets. Furthermore, we use the found facets to predict external outcomes and thereby provide evidences of criterion validity. We aim to test the following hypothesis, designed to replicate previous findings: 

* H1. SWL will be best predicted by the composites of Extraversion and Neuroticism. 
    + H1.1. Adding the facets will significantly improve the predictions of personality on SWL. 
    + H1.2. Particularly the facets *Confidence* (N2) and *Positive attitude* (E4) will behave similarly to those reported by @Schimmack2004. 
* H2. Conscientiousness will be the strongest dimension when predicting academic achievement. 
    + H2.1. Openness will be related positively but moderately to academic achievement.
    + H2.2. Facets will add about 10% of additional explained variance to dimensions when predicting academic achievement
    
* H3. Facets will improve the predictive power of dimensions when predicting school abseentism.


Furthermore, we aim to provide evidences on the research questions of which facets predominantly correlate with academic achievement and school abseentism. Measurement invariance across samples will be examined in the second study. To sum up, the aim for this research project was to provide an instrument that can be used in non-clinical but also in clinical research which emphasizes the facet level of the Big Five. 


# Methods

Two different studies are presented in this work. The first study uses a sample drawn from the USA bachelor student population. The aim was to detect and confirm a model that maximizes the facet space below the Big Five domains. Exploratory factor analysis (EFA) was used to identify the number of facets per domain. A confirmatory factor analysis (CFA) per facet was specified in order to confirm the item - facet relationship. An exploratory strucutural equation model (ESEM) was applied to test a full model in which the facets serve as indicators of the Big Five domains. ESEM has gained reputation in the personality field, where the independent cluster model may not capture the complexity of the constructs measured [@Marsh2010]. Finally, reliability measures for the facets and test-criterion correlations will be computed to achieve evidences of reliability and criterion validity.

The second sample is a sample representative for the German speaking population of Germany, Austria and Switzerland. The aim for the second study was to replicate the structure found in study one, plus assess the degree of measurement invariance of the proposed model.

## Study 1 - US-American Sample

### Participants
The sample consisted of `r  length(dt$age)` American undergraduate students (`r as.numeric(round(prop.table(table(as.factor(dt$sex)))[2], 3)*100)`% male) who participated voluntarily. The mean age was `r round(mean(dt$age),1) ` years (SD = `r round(sd(dt$age), 1)  `). Students were emailed a link to a computerized assessment battery that included the IPIP items as well as several other tests not reported in this paper.
The data set was randomly split into two equally sized samples. Both samples were matched in relation to missing values, outliers and extreme values. In Sample 1 the mean age was `r round(mean(dt$age[which(dt$id %in% sub1$respid)]), 1)  ` years (SD= `r round(sd(dt$age[which(dt$id %in% sub1$respid)]), 1)  `), in Sample 2 the mean age was `r round(mean(dt$age[which(dt$id %in% sub2$respid)]), 1)  ` years (SD=`r round(sd(dt$age[which(dt$id %in% sub2$respid)]), 1)  `).

## Measures

### Items from the International Personality Item Pool (IPIP)
Altogether, 525 items from the *International Personality Item Pool* (IPIP) were used to measure Neuroticism, Extraversion, Openness (to experience), Agreeableness and Conscientiousness. The IPIP is an open source database of personality items, which was launched in 1996, and contains over 2000 items [@Goldberg2006].
Participants were asked to rate themselves on typical behaviors or reactions on a 5-point Likert scale, ranging from 1 (“Not all like me”) to 5 (“Very much like me”).

The item selection was part of a different project and the procedure has been explained in detail in the appendix of a study by @MacCann2009. That study also contains part of the sample used here. However, the current data set contains more participants.

### Satisfaction With Life (SWL)
Measured with a 5 item composite defined in @Diener1985, answered in a 7 point Likert-type scale ranging from 1 (*strongly disagree*) to 7 (*strongly agree*). The items are: a)"In most ways my life is close to ideal", b) "The conditions of my life are excellent", c) "I am satisfied with my life", d) "So far I have gotten the important things in my life", and e) "If I could live my life over, I would change almost nothing". Psychometric properties have been reported excellent. (In which moment have SWLS been measured? just at the same time point than personality?)

### GPA
Grade Point Averages measured in high school, university, and in cc.

### SAT


### ACT


### Absences from class
As a behavioral measure absence from class was asked to report from subjects. ABS2 ABS4 what are the differences?


## 2.1.3. Procedure

### EFA with subsample 1
To determine the number of possible facets per domain @Velicer1976 Minimum Average Partial (MAP) method and @Horn1965 parallel analysis (PA) were employed for every domain. Based on these results an Exploratory Factor Analysis (EFA) was calculated for each domain via Mplus using a geomin rotation (Quelle) and a Maximum Likelihood estimator (ML). The decision for the preferred number of facets per domain was based partly on comparing model fits (CFI, RMSEA, SRMR). More importantly though was the interpretability of the facet solution. To this end, facet solutions from other personality measures were looked and compared to the found facet structure. If there were important parts missing to present the domain with regards to content, new facets were added a posteriori.

### CFA and ESEM with subsample 1
To confirm the structure of facets the EFAs delivered, multiple CFAs were calculated via Mplus. In a first step, measurement models were estimated for each of the facets. To obtain balance between the facets, the items were reduced to five per facet based on item content and loading pattern. In a second step, the estimations for the measurement models on facet levels were repeated via CFA. For both steps estimators were WLSMV (Weighted Least Squares adjusted for Means and Variances). Aim was to ensure an optimal breadth and sufficient reliability. In a final model, all five domain structural models were integrated using ESEM [@AsparouhovMuthen2009]. @Marsh2010 could show that ESEM fits personality data better and results in substantially more differentiated factors than CFA. All facets were allowed to load on all domains. If there would show up facets that do not significantly load on the intended domain, this facets would get eliminated subsequently. The estimator used was WLSMV, factor scores from the facet CFAs were used as indicators and the rotation was oblique (using Geomin). Model fit was determined based on the guide lines by @Hu1999 as well as @Beauducel2005. Consequently, to consider a good fit of a proposed model, the Comparative Fit Index (CFI) should be at or over .95, the Standardized Root Mean Squared Residual (SRMR) smaller than .08 and the Root Mean Square Error of Approximation (RMSEA) smaller than .06. For the ESEM models we compared our results with the findings by @Marsh2010.

## Reliability

Chronbach's $\alpha$ and McDonald's $\omega$ will be calculated for each facet to provide measures of internal consistency.

### Criterion validity evidence 

To examine the nomological structure of the facets and domains to external constructs, a set of linear models and correlations were fitted. We describe in this section the methods used to test the set of hypothesis described in the introduction. 

To explore H1 we explored the correlation matrix between Big Five dimensions and SWL. To explore H1.1. we fitted a two-step regression including the full set of dimensions in the first step and a selection of facets following a stepwise procedure in the second step. H1.2. will be inspected adding only N2 and E4 to the second step instead of the full set of facets. 

H2 and H2.1. will be tested by examining the correlation matrix of Conscientiousness and Openness with academic achievement. A stepwise regression will be used to test H2.2. Conscientiousness and Openness will be the first set of predictors and their respective facets will be entered in a second step, changes in $R^2$ will be inspected.

H3 will also be tested with a hierarchical regression in which the Big Five dimensions will be first entered and then a set of facets previously selected by stepwise regression from the full set.

The research questions will be commented by looking at which facets best predict academic achievement and scholastic absences.


## Results

### Results of EFA
In *Table 2* model fits for the chosen facet model for each domain are shown, as well as Eigenvalues and results from MAP and PA test.
To ensure the homogeneity of the facets and to reduce the risk of cross domain loadings, items with factor loadings less than .30 were eliminated. This was only done when item content was also judged as being non-central to the domain in question [@Ziegler2014]. 

\vspace{5mm}

< Table 2 here>

```{r table2, eval=F}
setwd(here("tables"))
table2 <- read_excel("table2.xlsx")
kable(table2, format = "latex", align = "l", booktabs = T, caption="Table 2. Results for the EFA on the Big Five domains")%>% 
  column_spec(1, width = "8em", bold = F, italic = F) %>% 
  column_spec(2, width = "8em", bold = F, italic = F)
```

\vspace{5mm}

According to the exploratory model, Agreeableness consists of eight facets after two facets were eliminated due to weakly loading and inconsistent items. The remaining facets were named *Appreciation*, *Integrity*, *Low competitiveness*, *Readiness to give feedback*, *Search for support*, *Good faith*, *Genuineness* and *Altruism*. 

Conscientiousness consists of nine facets after one facet with item factor loadings less than .30 was excluded, they are: *Dominance*, *Persistence*, *Self-discipline*, *Task planning*, *Goal orientation*, *Carefulness*, *Orderliness*, *Wish to work* (to capacity) and *Productivity*. 

Extraversion is formed by nine facets. A new facet (*Energy*) was added in order to tap better the physical component of Extraversion, which was missing in the eight facet solution. The facets are *Sociability*, *Readiness to take risks*, *Wish for affiliation*, *Positive attitude*, *Forcefulness*, *Communicativeness*, *Humor*, *Conviviality* and *Energy*.

Neuroticism (interpreted here as emotional stability) consists of seven facets. One facet was dropped due to poor interpretability, and was therefore not included in the subsequent analyses. The final set of facets are named *Equanimity*, *Confidence*, *Carefreeness*, *Mental balance*, *Drive*, *Emotional robustness* and *Self-attention*.

Openness to experience comprises nine facets. One facet was identified as a method factor and eliminated, because it solely contained negatively formulated items and no coherent underlying trait could be identified. Furthermore another facet (*Intellect*) was added, because the remaining facets lacked an intellectual content. The facets of Openness are named *Creativity*, *Wish for variety*, *Open-mindedness*, *Interest in reading*, *Artistic interests*, *Wish to analyze*, *Willingness to learn*, *Sensitivity* and *Intellect.*

The items to each facet are listed in the appendix (A).



### Results of CFA and ESEM
All measurement models for the facets fitted well, results are summarized in *Table 3*. In this table both models with five items only and models with all items are presented with their respective model fit. The 5-item facets normally outperform the models including all items regarding model fit.

\vspace{5mm}

< Table 3 here caption="Model fit for each facet")>

\vspace{5mm}

```{r table3, eval=F}
setwd(here("/tables"))
table3 <- read_csv("table3.csv")
table3 <- table3[,-c(7,12)]
colnames(table3) <- sub("_1","",colnames(table3))
colnames(table3) <- sub("_2","",colnames(table3))


  kable(table3, "latex", align = "l", booktabs = T, linesep="", longtable=T,caption = "Table 3. Model fit for each facet")%>%
  kable_styling(latex_options = "scale_down") %>%
  add_header_above(c(" " = 1, "Full items" = 5, "5 items" = 4, " " = 4)) %>%
  add_header_above(c(" " = 1, "USA sample" = 9, "German sample" = 4)) %>% 
      landscape() %>% 
  kable_styling(latex_options = "repeat_header")

```


The ESEM of the final model with all five domains yielded an acceptable fit [@Marsh2010]: CFI = .87, RMSEA = .072, SRMR = .036. As it can be seen in *Table 4* nearly all facets loaded significantly on their intended domain. Some cross loadings emerged as is typical for ESEM procedures.

\vspace{5mm}

< Table 4 here caption="ESEM factor scores")> 

\vspace{5mm}


### Reliability


```{r reliability, echo=F}
#Agreeableness
library(psych)
setwd(here("/data/Sample_USA_EFA+CFA/CFA/Agreeableness/5 Items"))
a <- list.files()[1:8]
arel <- tibble(alpha=NA, omega=NA)
for(i in 1:length(a)){
assign(paste(sub(".txt","",a[i])),read.table(a[i], header=F))
}
for(i in 1:length(a)){
arel[i,1] <- psych::alpha(get(paste("a", i, sep = ""))[,1:5], check.keys = T)$total$std.alpha
arel[i,2] <- psych::omega(get(paste("a", i, sep = ""))[,1:5], nfactors = 1)$omega.tot
}

#Conscientiousness
setwd(here("/data/Sample_USA_EFA+CFA/CFA/Conscientiousness/5 Items"))
c <- list.files()[2:10]
crel <- tibble(alpha=NA, omega=NA)
for(i in 1:length(c)){
assign(paste(sub(".txt","",c[i])),read.table(c[i], header=F))
}
for(i in 1:length(c)){
crel[i,1] <- psych::alpha(get(paste("c", i, sep = ""))[,1:5], check.keys = T)$total$std.alpha
crel[i,2] <- psych::omega(get(paste("c", i, sep = ""))[,1:5], nfactors = 1)$omega.tot
}

#Openness
setwd(here("/data/Sample_USA_EFA+CFA/CFA/Openness/5 Items"))
o <- list.files()[32:40]
orel <- tibble(alpha=NA, omega=NA)
for(i in 1:length(o)){
assign(paste(sub(".txt","",o[i])),read.table(o[i], header=F))
}
for(i in 1:length(o)){
    if( i ==9){    #some facets don't have 5 items, this is one example
      orel[i,1] <- psych::alpha(get(paste("o", i, sep = ""))[,1:3], check.keys = T)$total$std.alpha
      orel[i,2] <- psych::omega(get(paste("o", i, sep = ""))[,1:3], nfactors = 1)$omega.tot
    }else{
      orel[i,1] <- psych::alpha(get(paste("o", i, sep = ""))[,1:5], check.keys = T)$total$std.alpha
      orel[i,2] <- psych::omega(get(paste("o", i, sep = ""))[,1:5], nfactors = 1)$omega.tot
    }
}

#Neuroticism
setwd(here("/data/Sample_USA_EFA+CFA/CFA/Neuroticism/5 Items"))
n <- list.files()[26:32]
nrel <- tibble(alpha=NA, omega=NA)
for(i in 1:length(n)){
assign(paste(sub(".txt","",n[i])),read.table(n[i], header=F))
}
for(i in 1:length(n)){
  if( i ==7){    #n7 only 9 items
      nrel[i,1] <- psych::alpha(get(paste("n", i, sep = ""))[,1:3], check.keys = T)$total$std.alpha
      nrel[i,2] <- psych::omega(get(paste("n", i, sep = ""))[,1:3], nfactors = 1)$omega.tot
    }else{
nrel[i,1] <- psych::alpha(get(paste("n", i, sep = ""))[,1:5], check.keys = T)$total$std.alpha
nrel[i,2] <- psych::omega(get(paste("n", i, sep = ""))[,1:5], nfactors = 1)$omega.tot
}}

#Extraversion
setwd(here("/data/Sample_USA_EFA+CFA/CFA/Extraversion/5 Items"))
e <- list.files()[10:18]
erel <- tibble(alpha=NA, omega=NA)
for(i in 1:length(e)){
assign(paste(sub(".txt","",e[i])),read.table(e[i], header=F))
}
for(i in 1:length(e)){
    if( i ==9){   #e9 only 4 items
      erel[i,1] <- psych::alpha(get(paste("e", i, sep = ""))[,1:4], check.keys = T)$total$std.alpha
      erel[i,2] <- psych::omega(get(paste("e", i, sep = ""))[,1:4], nfactors = 1)$omega.tot
    }else{
erel[i,1] <- psych::alpha(get(paste("e", i, sep = ""))[,1:5], check.keys = T)$total$std.alpha
erel[i,2] <- psych::omega(get(paste("e", i, sep = ""))[,1:5], nfactors = 1)$omega.tot
}}
```

Reliabilities for the 5 item facets were calculated with $\alpha$ and $\omega$ estimates. Agreeableness showed a mean $\alpha$ of `r round(mean(arel$alpha),2)`, and a mean $\omega$ of `r round(mean(arel$omega),2)`. Conscientiousness' mean $\alpha$ = `r round(mean(crel$alpha),2)`, and mean $\omega$ = `r round(mean(crel$omega),2)`. Openness' mean $\alpha$ = `r round(mean(orel$alpha),2)`, and  mean $\omega$ = `r round(mean(orel$omega),2)`. Neuroticism mean $\alpha$ = `r round(mean(nrel$alpha),2)`, and mean $\omega$ = `r round(mean(nrel$omega),2)`. Extraversion's mean $\alpha$ = `r round(mean(erel$alpha),2)`, and mean $\omega$ = `r round(mean(erel$omega),2)`.


```{r table 4 esem1, results="asis", message=F, eval=F}
setwd(here("tables"))
mytable <- read_csv("table4.csv")
mytable <- mytable[,-1]
mytable$Agreeableness[1:6] <- paste("\\textbf{",mytable$Agreeableness[1:6], "}", sep="")
mytable$Conscientiousness[7:15] <- paste("\\textbf{",mytable$Conscientiousness[7:15], "}", sep="")
mytable$Extraversion[16:23] <- paste("\\textbf{",mytable$Extraversion[16:23], "}", sep="")
mytable$Neuroticism[24:30] <- paste("\\textbf{",mytable$Neuroticism[24:30], "}", sep="")
mytable$Openness[31:38] <- paste("\\textbf{",mytable$Openness[31:38], "}", sep="")
colnames(mytable)[1]<-"Facet"


# print(xtable(mytable, caption="ESEM factor scores USA sample"),include.rownames=FALSE, size="\\fontsize{9.5pt}{9pt}\\selectfont", caption.placement = "top",sanitize.text.function=Hmisc::latexTranslate)

kable(mytable, booktabs=T, escape=F, linesep="", align="l", caption = "Table 4. ESEM factor scores USA sample")

```

### Criterion validity evidence


```{r swl criterion, echo=F, message=F, warning=F}
library(here)
library(readxl)

setwd(here("data/ETS_IPIP/Datensätze"))

dt <- read_excel("ETS_regression.xlsx")
dth1 <- dt[,c(54, 47:51)]
dth1.1 <- dt[,c(54, 5:51)]
first <- lm(lifesat~sumsA+sumsC+sumsE+sumsN+sumsO, dth1.1)     
dth1.11<-dt[,c(54,5:46)]
set.facets <- step(lm(lifesat~.,dth1.11))
second <- lm(lifesat ~ sumsA1 + sumsC1 + sumsC4 + sumsC6 + sumsC7 + sumsE2 + 
    sumsE4 + sumsE9 + sumsN1 + sumsN2 + sumsN4 + sumsN5 + sumsO1 + 
    sumsO2 + sumsO8 + sumsO9 , dth1.11)
h1.1 <- anova(first, second)
third <- lm(lifesat ~ sumsN+sumsE+sumsN2 + sumsE4, dt)
h1.2 <- anova(first, third)

dth2hs <- dt[dt$hsgpa_num >0, c(53, 5:51)]

#step(lm(hsgpa_num ~ sumsO + sumsE+sumsN+sumsA+sumsC, dth2hs))
firsth2 <- lm(hsgpa_num ~ sumsC+sumsO+sumsN+sumsE+sumsA, dth2hs)
dth2hs2 <- dth2hs[,1:43]
secondh2 <- lm(hsgpa_num ~., dth2hs2)
h2 <- anova(firsth2,secondh2)


dth3 <- dt[,5:51]
dt$absences2[dt$absences2==-77] <- 0
dth3$abs <- log1p(dt$absences2)

firsth3 <- lm(abs~sumsN+sumsO+sumsA+sumsC+sumsE, dth3)
dth3.1 <- dth3[,-43:-47]
facetsh3 <- step(lm(abs~., dth3.1))
secondh3 <- lm(abs ~ sumsA1 + sumsA3 + sumsA7 + sumsC3 + sumsC5 + sumsC8 + sumsC9 + 
    sumsE1 + sumsE2 + sumsN1 + sumsN3 + sumsN5 + sumsO1 + sumsO2 + 
    sumsO3 + sumsO4 + sumsO5 + sumsO6, dth3.1)
h3 <- anova(firsth3,secondh3)
```


Our first set of hypothesis tested how personality was related to SWL. Extraversion (*r* = `r round(cor(dth1$lifesat, dth1$sumsE),2)`) and Neuroticism (*r* = `r round(cor(dth1$lifesat, dth1$sumsN),2)`) were the dimensions with higher correlations with SWL. In H1.1, the model which included the facets outperformed the dimension model (*F* = `r round(h1.1$F[2], 2)`, p < 0.001). The model resulted in a predictive gain of $\Delta R^2$ = `r round(summary(second)$r.squared - summary(first)$r.squared, 2)`. Adding N2 and E4 result in a predictive gain of $\Delta R^2$ = `r round(summary(third)$r.squared - summary(first)$r.squared, 2)`.

Our second set of hypothesis involves predictions to academic achievement. Conscientiousness correlated with academic achievement with *r* = `r  round(cor(dth2hs$hsgpa_num, dth2hs$sumsC),2)`, being the strongest correlation of all the set of dimensions. Openness correlated *r* = `r  round(cor(dth2hs$hsgpa_num, dth2hs$sumsO),2)` with the criterion. For H2.2, the model which included the facets again outperformed the dimensional model (*F* = `r round(h2$F[2], 2)`, p < 0.001), with a predictive gain of $\Delta R^2$ = `r round(summary(secondh2)$r.squared - summary(firsth2)$r.squared, 2)`.

Our thirst set of hypothesis explored the relationship of personality with school absences. The facet level model outperformed the dimensional level (*F* = `r round(h3$F[2], 2)`, p < 0.001), $\Delta R^2$ = `r round(summary(secondh3)$r.squared - summary(firsth3)$r.squared, 2)`. 



\vspace{5mm}

< Table 5 here caption="Criterion correlations" >


```{r table5, results="asis", eval=F}
setwd(here("tables"))

corsabrev <- read_csv("table5abrev.csv")

library(dplyr)
corsabrev %>%
  mutate_each(funs(cell_spec(., bold=ifelse(. >= .20 | . <= -.20, TRUE, FALSE))), -Facets) %>% 
  kable("latex",escape=F, booktabs=T, linesep="", align="l",caption="Table 5. Criterion correlations at the facet level") %>% 
  landscape(margin = "0cm") %>% 
  footnote(c("SWLS: Satisfaction With Life Scale.",
             "GPA: Grade Point Average, 'cc' = full academic career, 'univ' = university, 'hs'= High School.",
             "SAT: Scholastic Assessment Test, 't' = total, 'r' = reading test, 'm' = math test, 'w' = writing and language test.",
             "ACT: American College Testing, 't' = total, 'm' = math test, 'r' = reading test, 'w' = writing test, 's' = science test.",
             "ABS: Absences from school (?), 2 = correlation with 2 absences, 4 = correlation with 4 absences.",
             "Correlations above |.20| are shown in bold."), threeparttable=T, escape=F)


```

\vspace{5mm}


## Study 2 – German Sample


### Participants
The representative sample consisted of 387 German speakers (`r round(as.numeric(prop.table(table(de$SEX))[1]), 3)*100 `% male) with a mean age of `r round(mean(de$AGE),1)` years (SD = `r round(sd(de$AGE),1)`). The data was collected in a test center.

### Measures
The five items per facet derived from Study 1 were translated and back-translated by bilingual experts, creating a German version of the measure used there. The translated items can be found in appendix B.

## Procedure

### Step 1 – Examining the structure. 
To check the facet structure Study 1 delivered, multiple confirmatory factor analyses were calculated via Mplus following an analogue procedure to Study 1. First, measurement models were estimated for all facets, using WLSMV as the estimator. Model fit was determined based on the guide lines mentioned above. In a final model, all five domain structural models were integrated using ESEM.

### Step 2 – Testing for measurement invariance. 
In a next step, measurement invariance between German and US samples was examined. We followed the procedure suggested by @Sass2011 and tested configural, factorial and strong factorial invariance. The cutoffs suggested by @Chen2007 were applied to compare model fits. According to this configural measurement invariance can be assumed when the same item is associated with the same factor in each domain, while the factor loadings can differ. If the factor loadings of each item would not differ between the samples, factorial measurement invariance can be assumed. Strong factorial measurement invariance can be assumed when on top of that the intercepts of each item are equal. 
The limit to factorial measurement invariance was set to $\Delta$ CFI < .01, $\Delta$ RMSEA < .015 and $\Delta$ SRMR < .03, at which the limit to strong factorial measurement invariance was set to $\Delta$ CFI < .01, $\Delta$ RMSEA < .015, $\Delta$ SRMR < .01 as suggested by @Chen2007.


## Results

### Results of CFA 
The measurement models of the American sample were replicated for the reduced number of items per facet. Model fits can also be seen in *Table 3*. The ESEM with all five domains showed a relatively good fit to the data with CFI = .82, RMSEA = .078, SRMR = .044. *Table 6* shows the ESEM factor loadings for the German sample. All facets loaded significantly on their intended domain.


```{r table6, results="asis", eval=F}
setwd(here("tables"))
table6 <- read_csv("table6.csv")
# print(xtable(table6, caption="ESEM factor scores German sample"),include.rownames=FALSE, size="\\fontsize{9.5pt}{9pt}\\selectfont", caption.placement = "top",sanitize.text.function=Hmisc::latexTranslate)

colnames(table6)[1]<-"Facets"
# table6 <- table6[,c(1,2,3,4,6,5)]
# colnames(table6) <- c("Facets", "Agreeableness", "Conscientiousness", "Extraversion", "Neuroticism",
#                       "Openness")
kable(table6, booktabs=T, escape=F, linesep="", align="l", caption = "Table 6. ESEM factor scores German sample")
```
\vspace{5mm}

<Table 6 here > 

\vspace{5mm}

### Results of MI
For analyzing measurement invariance the latest facet model structure (with additional facets) was taken. The results are shown in Table 7.
Configural measurement invariance could be shown for the facets *Appreciation of others*, *Superiority/Grandiosity*, *Need to be liked*, *Crybabiness*, *Manipulation*, *Altruism* (facets of Agreeableness), *Perseverance*, *Task Planning*, *Goal-orientation/Achievement striving*, *Preferred Load*, *Procrastination* (facets of Conscientiousness), *Assertiveness*, *Sociability/Gregariousness*, *Activity* (facets of Extraversion), *Irritability*, *Self-serving Attention* (facets of Neuroticism), *Self-attributed Inginuity*, *Openness to actions and activities*, *Openmindedness/Judgement*, *Love of Learning*, *Openness to feelings* and *Intellect* (facets of Openness).

Factorial measurement invariance could be shown for the facets *Meanness*, *Trust* (facets of Agreeableness), *Control of others*, *Lack of (Self-) Control*, *Deliberation/Caution*, *Lack of Tidiness/Order* (facets of Conscientiousness), *Sensation Seeking*, *Reclusiveness*, *Emotionality*, *Humor* (facets of Extraversion), *Depression*, *Anxiety*, *Self-assuredness*, *Lethargia*, *Sentimentality* (facets of Neuroticism), *Openness to reading*, *Openness to arts* and *Need for cognition* (facets of Openness).

The only facet with strong factorial measurement invariance was *Shyness*, a facet of Extraversion


```{r table7, eval=F}
setwd(here("tables"))
table7 <- read_excel("table7.xlsx", col_names = T)
table7[is.na(table7)]<-""
colnames(table7)[1] <- ""

kable(table7, "latex", align = "l", booktabs = T, linesep="", caption = "Measurement invariance") %>% 
  kable_styling(latex_options = "scale_down")
```

\vspace{5mm}

<Table 7 here>

\vspace{5mm}

# Discussion

We have presented in this work an open-access instrument for personality assessment within the Big Five framework, which showed evidences of factorial validity in two different cultures and maximized the space set of facets encompassed. With a modest number of items (202) by comparison with the most influential Big Five inventories presented in *Table 1*, we have reached to a large set of facets which mostly show a robust factorial validity in both studies, as shown in *Table 3*. 

The Big Five solution has been recognized as the most replicable model for personality inventories, reaching a hallmark of consensus in personality science for the last decades. However, some researchers have pointed out that while the Big Five has repeatedely been found when fitting EFA to personality data, its replicability under CFA procedures has been more elusive [@McCrae1996]. The constriction of the common independent cluster solution, where cross-loadings are restricted to zero, may suppose a rather strong assumption for personality trait inventories [@Marsh2010]. The idea of facets, or habits, being influenced by more than one domain can definitely make some sense. ESEM helps overcoming this assumption and provides a measure about how well the Big Five solution adjusts to the data. Using this procedure, the degree of integration of our proposed set of facets to the Big Five factor solution has been solid enough according to the cut-off values proposed by @Marsh2010. The number of significant cross-loadings in the ESEM models has not been large either, advocating a good discriminant validity.

The instrument presented in this work covers all the "core" facets proposed by @SotoJohn2009, either directly or indirectly. The *Energy* construct in Extraversion is literally covered by a three-item facet in our instrument, whereas the *Assertiveness* construct has been tapped by items belonging to the *Wish for affiliation*, *Communicativeness* and *Conviviality* facets. *Altruism* is directly reflected in a five-item facet, while the *Compliance* construct is reflected by our *Good faith* facet. The *Order* and *Self-discipline* constructs proposed by @SotoJohn2009 are mirrored by dedicated facets in our instrument. The *Anxiety* and *Depression* constructs are mirrored by the facets *Mental balance* and *Emotional robustness*, respectively. For the *Openess* dimension, the *Aesthetic* contruct is covered by our facet *Artistic interest*, while the *Ideas* construct has been reflected by both the *Open-mindedness* and the *Wish to analyze* facets. The two-per-facet components proposed by @DeYoung2007 were also being tapped by the set of facets in our inventory.


The instrument covers most of facets proposed by the most influential Big Five measures as seen in *Table 1*. The most salient differences are related to the HEXACO model, which entails a six factor solution with a slightly different theoretical conceptualization [@Lee2006]. Most notably 


Although these facets are not being covered directly in our inventory, components of facets from distinct domains in our model retain a glimpse of the missing facets. This underlies the importance of allowing cross-loadings for trait personality data. Let's use the example of *Patience*, a facet proposed in the HEXACO model for the Agreeableness domain which is not covered in our instrument, nor in the other three Big Five inventories which have been revised. Although patience, there is a notion of a patient trait within the *Self-discipline* facet in the Conscientiousness domain, specially with items such as "I rush into things" or "I act impulsively when something is bothering me" (See appendix A). In fact, *Self-discipline* has important cross-loadings with Agreeableness in both samples ($\lambda$ = .256 in the USA sample and $\lambda$ = .341 in the german sample). 


In addition we included even more facets.

In addition, evidences for external criteria validity were attained. 


We have collected some criterion validity evidences. Like bla bla bla. Nonetheless the multi - facetted nature of the instrument makes forthcoming evidences for criterion and predictive validity promising.

One limitation is the sample used. Students are not a representative population of society and results may not be generalized. 

Future directions are to provide a tool with the subset of items for public use. Gather community sample, from more cultures and test the extent of the universality of the instrument. And use the instrument to predict important life outcomes so the links between specific behaviors and facets become richer.


\newpage

Remove this page. This is used to include the tables' references into the bibliography.

@Brick2014; @Gaughan2012; @Leone2012; @Mcabee2014; @Gaughan2009; @Noftle2006; @Bagby1994; @Schimmack1999; @Wakabayashi2006; @Shaver1992; @Ruiz2003; @Mccrae2011; @Rosander2011; @McAdams2009; @Siddiqui2011; @Hagger-Johnson2007

@Ziegler2014

\newpage

```{r appendix A, results="asis", eval=F}
library(here)
library(readxl)
library(tidyverse)
library(kableExtra)
setwd(here("tables"))
key <- read_excel("appendix key.xlsx")
key$Domain<-ifelse(is.na(key$Domain), " ", key$Domain)
# key <- sub("\n", "",key$Item)
# strsplit(key$Item, "\n", fixed=T)
mutate_all(key,linebreak) %>% 
  kable(booktabs = T, escape = F, longtable=T, align="l", 
        linesep = '\\addlinespace', caption="Items of the new measure and their corresponding facets and domains")%>% 
  kable_styling(latex_options = "repeat_header")
```


# References
```{r create_r-references}
r_refs(file = "r-references.bib")
```

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id = "refs"></div>
\endgroup

